### 2019-03-18 message-from-committee.tex
message-from-committee.tex: Tweak participation ribbon footnote

Greetings friends, colleagues, and complete strangers. It is with great pride that we welcome you to the 0xDth annual Special Interest Group on Harry Q. Bovik, held in celebration of Harry Q Bovik's $10^{somenumberbiggerthan2}$th birthday. Normally this is where we, the ``committee'', would wax poetic about  features added\footnote{despite my effort to do away with the formulaic, the proceedings chair insisted I add an explanation of the artifact medal [medal here], given to all papers determined after careful scrutiny to have included a genuine artifact}, records broken, and facts fun. However, this year, we have decided to take the highly efficient and not at all lazy route of delegating the task of writing this message to committee members of the past. A sort of temporal passing of the buck, one might say. Thus I present to you, in reverse chronological order, some messages.

>>>>

Greetings friends, colleagues, and complete strangers. It is with great pride that we welcome you to the 0xDth annual Special Interest Group on Harry Q. Bovik, held in celebration of Harry Q Bovik's $10^{somenumberbiggerthan2}$th birthday. Normally this is where we, the ``committee'', would wax poetic about  features added\footnote{Despite my noble intention to dispatch with the labored, formulaic frontmatter of yestersyear, I was thwarted by a proceedings chair who insisted that I add an explanation of the unwittily-named ``unwitting participation ribbon'' (\,\raisebox{-0.25\height}{\includegraphics[height=3ex]{participation}}), an unwelcome brand we've affixed to each paper determined after careful scrutiny to have included a genuine artifact, thereby furthering the admirable causes of open science and fruitful procrastination.}, records broken, and facts fun. However, this year, we have decided to take the highly efficient and not at all lazy route of delegating the task of writing this message to committee members of the past. A sort of temporal passing of the buck, one might say. Thus I present to you, in reverse chronological order, some messages.
